Computer Science House Constitution

### 2024-03-26 constitution.tex
added one sentence to clarify membership status during conditional (#164)
136 removing dry notes (#163)
* ,

moved contents of the 'note' and 'additional note'

* removed\added \hfill\break for a newline command

* tried to fix the extraneous skill issues that I had

* skill issues again

* theoretically everything should be okay now, I nuked my const.tex file with the master one then made the changes I was supposed to make moving the contents of note and additional note

---------

Co-authored-by: ikopke23 <144629825+ik6335@users.noreply.github.com>

\asubsubsection{Selection Processes}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters

% Current RIT students is defined as students who have attended RIT for at least 1 full semester
\asubsubsubsection{Selection Process for Current RIT Students}
\begin{enumerate}
	\item The applicant submits an application to the Evaluations Director for review.
	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
	\item The application materials are then reviewed at an Evaluations meeting.
	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an Introductory Member.
\end{enumerate}
Note: Most membership privileges do not initiate until successful completion of the introductory process.
This means that until the member has passed the Introductory Evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
The member does, however, have the right to use Computer Science House's facilities.
The member is not required to pay dues during the Introductory Process.
\\* \\*
Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.

% Incoming RIT students is defined as students who have attended RIT for less than 1 full semester
\asubsubsubsection{Selection Process for Incoming RIT Students}
\begin{enumerate}
	\item During Spring semester, the Evaluations Director selects a group of Active Members to form a Selections Committee.
		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
        \item A subset of applicants will be offered Introductory Membership and must participate in the Introductory Process defined in \ref{The Introductory Process}. 
            A subset of Introductory Members will be offered On-Floor status and will be able to select a room on floor. 
            The other Introductory Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
\end{enumerate}
Note: Most membership privileges do not initiate until successful completion of the introductory process.
This means that until the member has passed the Introductory Evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
The member does, however, have the right to use Computer Science House's facilities.
The member is not required to pay dues during the Introductory Process.
\\* \\*
Additional Note: No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.

@@

\asubsubsubsubsection{Outcomes}
Members who pass Membership Evaluation have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
\\* \\*
If a member fails and has never passed a Membership Evaluation in the past, their membership will be revoked immediately.
If the member has previously passed a Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
In either case, the member forfeits their ability to be included on the following year’s roster.
\\* \\*
A member may be given a conditional to complete as a means of making up for missing requirements.
A conditional may be proposed by any member present at the Evaluation.
If the conditional is approved by the Evaluations Director, it is then voted on by House.
Each conditional consists of a set of additional requirements a deadline for completing them.
When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
A conditional member who does not meet these additional requirements will have failed the evaluation.
\asubsubsubsection{Appeals Process}
If a member disagrees with the outcome of any evaluation, (e.g. is not asked to return to the House for the following year) and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
\\* \\*
If the member is still unsatisfied after being heard by the Executive Board, the appeal may be brought to the attention of the ResLife Advisor.

>>>>

\asubsubsection{Selection Processes}
\renewcommand{\theenumi}{\alph{enumi}} % For this section, we want items to use letters
\hfill\break\hfill\break
Most membership privileges do not initiate until successful completion of the introductory process.
This means that until the member has passed the Introductory Evaluation, the member does NOT have the right to vote on House issues and does NOT count towards quorum.
The member does, however, have the right to use Computer Science House's facilities.
The member is not required to pay dues during the Introductory Process.
\\* \\*
No hazing shall occur at any time during the Selection Process in accordance with the New York State Hazing Laws.

% Incoming RIT students is defined as students who have attended RIT for less than 1 full semester

% Current RIT students is defined as students who have attended RIT for at least 1 full semester
\asubsubsubsection{Selection Process for Current RIT Students}
\begin{enumerate}
	\item The applicant submits an application to the Evaluations Director for review.
	\item The applicant participates in an informal interview with exactly three current Active, Alumni, or Honorary Members.
	\item The application materials are then reviewed at an Evaluations meeting.
	Then a simple majority vote, of attending members, is held on whether or not to accept the person as an Introductory Member.
\end{enumerate}
\asubsubsubsection{Selection Process for Incoming RIT Students}
\begin{enumerate}
	\item During Spring semester, the Evaluations Director selects a group of Active Members to form a Selections Committee.
		The Selections Committee reviews applications and conducts interviews in accordance with the process prescribed by Residence Life.
        \item A subset of applicants will be offered Introductory Membership and must participate in the Introductory Process defined in \ref{The Introductory Process}. 
            A subset of Introductory Members will be offered On-Floor status and will be able to select a room on floor. 
            The other Introductory Members will have Off-Floor status, but will otherwise have the same privileges and responsibilities.
\end{enumerate}

@@

\asubsubsubsubsection{Outcomes}
Members who pass Membership Evaluation have the option to participate as an Active Member in the following year and remain on the upcoming roster if applicable.
\\* \\*
If a member fails and has never passed a Membership Evaluation in the past, their membership will be revoked immediately.
If the member has previously passed a Membership Evaluation they will move to Alumni Membership status at the end of the Standard Operating Session (\ref{Alumni Membership Selection}).
In either case, the member forfeits their ability to be included on the following year’s roster.
\\* \\*
A member may be given a conditional to complete as a means of making up for missing requirements.
A conditional may be proposed by any member present at the Evaluation.
If the conditional is approved by the Evaluations Director, it is then voted on by House.
Each conditional consists of a set of additional requirements a deadline for completing them.
Members who are given a conditional have their evaluation decision deferred, and therefore maintain their current membership status until the conditional is resolved.
When the deadline expires, the conditional will be brought before the Executive Board who will assess its completeness.
A conditional member who does not meet these additional requirements will have failed the evaluation.
\asubsubsubsection{Appeals Process}
If a member disagrees with the outcome of any evaluation, (e.g. is not asked to return to the House for the following year) and wishes to appeal the decision, they may do so as stated in \ref{Appeals}.
\\* \\*
If the member is still unsatisfied after being heard by the Executive Board, the appeal may be brought to the attention of the ResLife Advisor.
